---
title: "Analysis of Experiment 3"
author: "Joern Alexander Quent"
date: "29/01/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

# Libraries
library(plyr)
library(ggplot2)
library(cowplot)
library(gridExtra)
library(grid)
library(knitr)
library(assortedRFunctions)
library(kableExtra)
library(MRColour)
library(jsonlite)
library(reshape2)
library(latex2exp)
library(lmerTest)
library(ez)
library(BayesFactor)
theme_set(theme_grey()) 
```

Note the analysis here only includes O-shaped rooms. 

Current balance: £147.04

# Results
```{r}
exp3_path <- "~/boundaryVR/data/Exp3/batch1/"
```

## Responses during video
### Video 1
```{r video_load_data}
# Get files
folder         <- '/show_video1/'
allFiles       <- list.files(paste0(exp3_path, folder))
allFiles_paths <- paste0(exp3_path, folder, allFiles)
n              <- length(allFiles_paths)

# Var
worker_id               <- c()
studyResultId            <- c()
vid_ext                  <- c()
subjCond                 <- c()
counterbalance_condition <- c()
num_keyPress             <- c()
movie                    <- c()
subjCond_corr            <- c()
movide_corr              <- c()
# Add video name
# Loop through all files
for(i in 1:n){
  jsonString                  <- readChar(allFiles_paths[i], file.info(allFiles_paths[i])$size)
  resultsList                 <- fromJSON(jsonString)
  worker_id[i]                <- resultsList$workerId
  studyResultId[i]            <- resultsList$studyResultId
  vid_ext[i]                  <- resultsList$vid_ext
  subjCond[i]                 <- resultsList$subjCond
  counterbalance_condition[i] <- resultsList$counterbalance_condition
  num_keyPress[i]             <- length(resultsList$whichKey)
  # Extract the the movie number
  movie[i]                    <- as.numeric(substr(resultsList$movie, nchar(resultsList$movie), nchar(resultsList$movie)))
  
  # Create response data.frame if number of responses is above one
  if(num_keyPress[i] > 1){
    tempDF <- data.frame(worker_id = worker_id[i], 
                         studyResultId = studyResultId[i],
                         keyPressed = resultsList$whichKey, 
                         timeStamp = resultsList$timeStamps)
    
    if(i == 1 | !exists('df_video_exp3')){
      df_video_exp3 <- tempDF
    } else {
      df_video_exp3 <- rbind(df_video_exp3, tempDF)
    }
    }
}




# Create aggregate info df
df_video_exp3_info <- data.frame(worker_id,
                                 studyResultId, 
                                 vid_ext,
                                 subjCond,
                                 counterbalance_condition,
                                 movie,
                                 num_keyPress)

# Calculate inter-response intervals
df_video_exp3_intervalls <- ddply(df_video_exp3, 
                                  c('worker_id', 'studyResultId'), 
                                  mutate,
                                  IRI = c(diff(timeStamp), NA))

df_video_exp3_intervalls_agg <- ddply(df_video_exp3_intervalls, 
                                      c('worker_id', 'studyResultId'), summarise,
                                      meanIRI = mean(IRI, na.rm = TRUE),
                                      sdIRI   = sd(IRI, na.rm = TRUE),
                                      n       = length(IRI))

not44   <- round(mean(df_video_exp3_info$num_keyPress != 44)*100, 1)
below44 <- round(mean(df_video_exp3_info$num_keyPress < 44)*100, 1)
```

For `r not44` %  of participants we didn't register the 44 responses. Some of this issue due to the fact that if the key is pressed to long multiple response are registered. Only `r below44` of all, gave fewer than 44 responses. Therefore it seems that compliance is quite good. Also note that here we also include people who might not did or might be excluded from the memory analysis.

```{r video_response_analysis}
# People that have given 44 responses
include <- df_video_exp3_intervalls_agg$worker_id[df_video_exp3_intervalls_agg$n == 44]

# Create subset
df_video_exp3_sub <- df_video_exp3[df_video_exp3$worker_id %in% include, ]

# Calculate inter-response intervals
df_video_exp3_intervalls <- ddply(df_video_exp3_sub, 
                                  c('worker_id', 'studyResultId'), 
                                  mutate,
                                  IRI = c(diff(timeStamp), NA))

df_video_exp3_intervalls_agg <- ddply(df_video_exp3_intervalls, 
                                      c('worker_id', 'studyResultId'), summarise,
                                      meanIRI = mean(IRI, na.rm = TRUE),
                                      sdIRI   = sd(IRI, na.rm = TRUE),
                                      n       = length(IRI))

mean_IRI <- mean(df_video_exp3_intervalls_agg$meanIRI)
sd_IRI   <- sd(df_video_exp3_intervalls_agg$meanIRI)
```

As expected, those people who gave 44 response give around the same time. The average inter-response-interval (IRI) is `r mean_SD_str(mean_IRI, sd_IRI, 0)` msec (SD in brackets). This tiny SD is not unexpected as the time between objects was the same for all participants. 


One way of checking whether participants are paying attention to the video is to correlate their responses to the responses of everyone else. To make things easier, I just do this with people who have given exactly 44 responses as I don't want to fiddle around with removing multiple responses. 

```{r corr_anlysis_video}
# Binarise for correlation
df_video_exp3_sub$smaller <- 0
df_video_exp3_sub$smaller[df_video_exp3_sub$keyPressed == 108] <- 1

# Add object id
df_video_exp3_sub <- ddply(df_video_exp3_sub, c('worker_id '), mutate, obj_id = 1:44)

# Go through all participants and calculate correlation
workers         <- unique(df_video_exp3_sub$worker_id)
corr_per_worker <- c()

# Loop through all worker
for(i in 1:length(workers)){
  # Calculate correlation for this worker
  worker <- workers[i]
  
  # Calculate average response for everyone else
  everyone_else    <- df_video_exp3_sub[df_video_exp3_sub$worker_id != worker, ]
  average_response <- ddply(everyone_else, c('obj_id'), summarise, smaller = mean(smaller))
  
  # Calculate correlation with everyone else
  corr_per_worker[i] <- cor(df_video_exp3_sub$smaller[df_video_exp3_sub$worker_id == worker],
                            average_response$smaller) 
}

corr_range <- round(range(corr_per_worker), 2)
```

This procedure works quite well. The correlations for this subset of all participants who watch the video ranges between r `r rValue(corr_range[1])` and r `r rValue(corr_range[2])`.

```{r corr_bootstrap}
nIter <- 100000

average_response <- ddply(df_video_exp3_sub, c('obj_id'), summarise, smaller = mean(smaller))
bootstrap_corr <- c()

for(i in 1:nIter){
  # Calculate correlation with everyone else
  bootstrap_corr[i] <- cor(sample(c(0, 1), 44, replace = TRUE),
                            average_response$smaller) 
}

cut_off <- round(quantile(bootstrap_corr, 0.95), 2)
```

If I bootstrap responses by randomly sampling 0 and 1, the upper 95% value is r `r rValue(cut_off)`, which means that each subject for which I estimated this congruency is well above that. 

## Memory task
```{r memory_load_data}
# Get all files
folder1         <- '/memoryTask1/'
folder2         <- '/memoryTask2/'
allFiles1       <- list.files(paste0(exp3_path, folder1))
allFiles2       <- list.files(paste0(exp3_path, folder2))
allFiles1_paths <- paste0(exp3_path, folder1, allFiles1)
allFiles2_paths <- paste0(exp3_path, folder2, allFiles2)
n1              <- length(allFiles1_paths)
n2              <- length(allFiles2_paths)

# Half 1 
for(i in 1:n1){
  ############
  # Loading daya
  tempDF <- read.csv(allFiles1_paths[i], header = TRUE, na.strings = '')
  
  # Recode key presses
  response      <- rep(NA, nrow(tempDF))
  response[tempDF$key_press == 49] <- 1
  response[tempDF$key_press == 50] <- 2
  response[tempDF$key_press == 51] <- 3
  tempDF$response                  <- response
  
  # Convert RT to numeric  
  tempDF$rt <- suppressWarnings(as.numeric(as.character(tempDF$rt)))
  
  ############
  # Temporal order memory 1
  temporalOrder1 <- subset(tempDF, test_part == 'temporalOrder')
  
  # Calculate accuracy 
  accuracy <- rep(NA, nrow(temporalOrder1))
  accuracy[temporalOrder1$response == temporalOrder1$corr_resp] <- 1
  accuracy[temporalOrder1$response != temporalOrder1$corr_resp] <- 0
  temporalOrder1$accuracy <- accuracy
  
  # Create variable that describe whether target, foil1, foil2 was chosen
  choice <- rep('Target', nrow(temporalOrder1))
  choice[temporalOrder1$response == temporalOrder1$foil1Pos] <- 'Foil 1'
  choice[temporalOrder1$response == temporalOrder1$foil2Pos] <- 'Foil 2'
  temporalOrder1$choice <- choice
  
  
  # Create or bind to data.frame
  if(i == 1){
    df_order_exp3_h1    <- temporalOrder1
    df_order_exp3_h1$id <- i
  } else {
    temporalOrder1$id <- i
    df_order_exp3_h1      <- rbind(df_order_exp3_h1, temporalOrder1)
  }
}

# Half 2
for(i in 1:n2){
  ############
  # Loading daya
  tempDF <- read.csv(allFiles2_paths[i], header = TRUE, na.strings = '')
  
  # Recode key presses
  response      <- rep(NA, nrow(tempDF))
  response[tempDF$key_press == 49] <- 1
  response[tempDF$key_press == 50] <- 2
  response[tempDF$key_press == 51] <- 3
  tempDF$response                  <- response
  
  # Convert RT to numeric  
  tempDF$rt <- suppressWarnings(as.numeric(as.character(tempDF$rt)))
  
  ############
  # Temporal order memory 1
  temporalOrder1 <- subset(tempDF, test_part == 'temporalOrder')
  
  # Calculate accuracy 
  accuracy <- rep(NA, nrow(temporalOrder1))
  accuracy[temporalOrder1$response == temporalOrder1$corr_resp] <- 1
  accuracy[temporalOrder1$response != temporalOrder1$corr_resp] <- 0
  temporalOrder1$accuracy <- accuracy
  
  # Create variable that desribe whether target, foil1, foil2 was choosen
  choice <- rep('Target', nrow(temporalOrder1))
  choice[temporalOrder1$response == temporalOrder1$foil1Pos] <- 'Foil 1'
  choice[temporalOrder1$response == temporalOrder1$foil2Pos] <- 'Foil 2'
  temporalOrder1$choice <- choice
  
  
  # Create or bind to data.frame
  if(i == 1){
    df_order_exp3_h2    <- temporalOrder1
    df_order_exp3_h2$id <- i
  } else {
    temporalOrder1$id <- i
    df_order_exp3_h2    <- rbind(df_order_exp3_h2, temporalOrder1)
  }
}


df_order_exp3 <- rbind(df_order_exp3_h1, df_order_exp3_h2)
df_order_exp3$half <- factor(df_order_exp3$half, levels = c(0, 1), labels = c('h1', 'h2'))

df_order_exp3$context <- factor(df_order_exp3$context, levels = c('across', 'within'), labels = c('across', 'within'))
```


```{r memory_outlier}
# Outlier detection
outlier_data <- ddply(df_order_exp3, c('worker_id'), summarise, accuracy = mean(accuracy), rt = mean(rt))
outlier_data$trans_acc         <- arcsine_transform(outlier_data$accuracy)
outlier_data$trans_acc_outlier <- mad_outlier(outlier_data$trans_acc, 2)
outlier_data$rt_outlier        <- mad_outlier(outlier_data$rt, 3)

# Outlier removal
df_order_exp3 <- df_order_exp3[!(df_order_exp3$worker_id %in% c(15177, outlier_data[outlier_data$trans_acc_outlier == 1, 'worker_id'])), ] 
# 15177 Didn't do whole task

excluded <- round(mean(outlier_data$trans_acc_outlier)*100, 1)
```

Average transformed (overall) accuracy is treated as an outlier if it's above/below 2 median absolute deviations from the median. The let to the exclusion of `r excluded` % of the data. 

```{r memory_analysis1}
agg1 <- ddply(df_order_exp3, c('worker_id', 'subjCond', 'half','context'), summarise, accuracy = mean(accuracy), rt = mean(rt))
agg2 <- ddply(df_order_exp3, c('worker_id', 'subjCond','context'), summarise, accuracy = mean(accuracy), rt = mean(rt))

agg2$trans_acc <- arcsine_transform(agg2$accuracy)
agg1$trans_acc <- arcsine_transform(agg1$accuracy)

acc_p1 <- ggplot(agg2, aes(x = context, y = trans_acc)) + geom_hline(yintercept = arcsine_transform(1/3)) +
  geom_line(aes(group = worker_id)) +
  geom_point() + 
  geom_boxplot() + 
  stat_summary(geom = "point", fun.y = "mean", col = "black", size = 3, shape = 24, fill = "red") + 
  labs(title = 'Memory performance by condition', y = "arcsine(3AFC accruacy)", x = 'Context')

rt_p1 <- ggplot(agg2, aes(x = context, y = rt)) +
  geom_line(aes(group = worker_id)) +
  geom_point() + 
  geom_boxplot() + 
  stat_summary(geom = "point", fun.y = "mean", col = "black", size = 3, shape = 24, fill = "red") + 
  labs(title = 'RT by condition', y = "RT in msec", x = 'Context')

plot_grid(acc_p1, rt_p1)
```


```{r memory_analysis2}
test1 <- ttestBF(agg2[agg2$context == 'within', "trans_acc"], 
                 agg2[agg2$context == 'across', "trans_acc"], 
                 paired = TRUE, 
                 nullInterval = c(-Inf, 0))

test2 <- ttestBF(agg2[agg2$context == 'within', "rt"], 
                 agg2[agg2$context == 'across', "rt"], 
                 paired = TRUE, 
                 nullInterval = c(-Inf, 0))

n_analysed <- length(agg2[agg2$context == 'within', "trans_acc"])
```

I analyse the data (N = `r n_analysed`) above with a paired and directed t-test. For accuracy the result is $BF_{01}$ = `r reportBF(1/test1[2])` and for RT the result is $BF_{01}$ = `r reportBF(1/test2[1])`. So there is small evidence against an effect.

```{r}
diff_score <- agg2[agg2$context == 'within', "trans_acc"]-  agg2[agg2$context == 'across', "trans_acc"]

ggplot(as.data.frame(diff_score), aes(diff_score)) + geom_density() + labs(title = 'Distribution of difference scores', x = 'within - across', y = 'Density')
```

The distribution of difference seems to be fairly focussed around zero. 


In the following, I am trying to dissect the memory effect a bit. First, there is no difference between the counterbalancing conditions.

```{r memory_analysis3}
ggplot(agg2, aes(x = context, y = trans_acc)) + geom_hline(yintercept = arcsine_transform(1/3)) +
  facet_grid(~ subjCond) +
  geom_line(aes(group = worker_id)) +
  geom_point() + 
  geom_boxplot() + 
  stat_summary(geom = "point", fun.y = "mean", col = "black", size = 3, shape = 24, fill = "red") + 
  labs(title = 'Memory performance by condition by counterbalancing', y = "arcsine(3AFC accruacy)", x = 'Context')

```

Furthermore, there doesn't seems to be a difference between first memory test and the second memory test. 

```{r memory_analysis4}
ggplot(agg1, aes(x = context, y = trans_acc)) + geom_hline(yintercept = arcsine_transform(1/3)) +
  facet_grid(~ half) +
  geom_line(aes(group = worker_id)) +
  geom_point() + 
  geom_boxplot() + 
  stat_summary(geom = "point", fun.y = "mean", col = "black", size = 3, shape = 24, fill = "red") + 
  labs(title = 'Memory performance by condition by half', y = "arcsine(3AFC accruacy)", x = 'Context')

```

```{r rt_mem_corr}
rt_mem_corr_data <- outlier_data[outlier_data$trans_acc_outlier == 0,]
rt_mem_corr <- cor.test(rt_mem_corr_data$rt, rt_mem_corr_data$trans_acc)
```

There is a correlation between average RT and average accuracy r `r rValue(rt_mem_corr$estimate)`, p `r pValue(rt_mem_corr$p.value)`. 

```{r}
ggplot(rt_mem_corr_data, aes(x = rt, y =trans_acc )) + 
  geom_point() + 
  geom_smooth(method = 'lm') +
  labs(title = 'Correlation between accuracy and RT', x = "RT in msec", y = "arcsine(3AFC accruacy)")
```

### Additional memory analysis
```{r tableAnlysis}
df_order_exp3$targetTable <- ifelse(df_order_exp3$probeTable == 2, 3, 2)

# Is foil 1 and foil 2 on same table as target?
df_order_exp3$foil1_sameTable <- df_order_exp3$targetTable == df_order_exp3$foil1Table 
df_order_exp3$foil2_sameTable <- df_order_exp3$targetTable == df_order_exp3$foil2Table 

df_order_exp3_table <- ddply(df_order_exp3, c('id', 'context', 'foil1_sameTable', 'foil2_sameTable'), 
                       summarise,
                       acc   = mean(accuracy))

# Making one variable
sameTable <- rep('none', nrow(df_order_exp3_table))
sameTable[df_order_exp3_table$foil1_sameTable == TRUE & df_order_exp3_table$foil2_sameTable == FALSE] <- 'Foil 1 only'
sameTable[df_order_exp3_table$foil1_sameTable == FALSE & df_order_exp3_table$foil2_sameTable == TRUE] <- 'Foil 2 only'
sameTable[df_order_exp3_table$foil1_sameTable == TRUE & df_order_exp3_table$foil2_sameTable == TRUE] <- 'Both'

df_order_exp3_table$sameTable <- sameTable
df_order_exp3_table$trans_acc <- arcsine_transform(df_order_exp3_table$acc)

ggplot(df_order_exp3_table, aes(x = sameTable, y = trans_acc, fill = sameTable)) +
  facet_grid(~context) +
  geom_jitter(width = 0.1, height = 0, show.legend = FALSE) +
  geom_boxplot(alpha = 0.5, outlier.shape = NA, show.legend = FALSE) +
  geom_hline(yintercept = arcsine_transform(1/3)) +
  annotate('text', x = 1, y = arcsine_transform(1/3) -0.5, label = 'Chance') + 
  stat_summary(geom = "point", fun.y = "mean", col = "black", size = 3, shape = 24, fill = "red") +
  labs(y = 'arcsine(3AFC accuracy)', x = 'Foils on same table/position', title = 'Accuracy by foils on the same table')
```

```{r}
model <-glmer(accuracy ~ context*foil1_sameTable*foil2_sameTable +  (1| worker_id), data = df_order_exp3, family = 'binomial')

table1 <- createResultTable(model)
kable(table1)
```

```{r analyseInteraction,eval = TRUE}
df_order_exp3_interaction <- ddply(df_order_exp3, c('worker_id', 'context', 'foil2_sameTable'), summarise, accuracy = mean(accuracy))

ggplot(df_order_exp3_interaction, aes(x = context, y = accuracy))  +
  facet_grid(~ foil2_sameTable) +
  geom_jitter(width = 0.1, height = 0, show.legend = FALSE) +
  geom_boxplot(alpha = 0.5, outlier.shape = NA, show.legend = TRUE) + 
  stat_summary(geom = "point", fun.y = "mean", col = "black", size = 3, shape = 24, fill = "red") +
  labs(title = 'Accuracy as function of whether foil 2 is at the same table')
```

## Debrief
```{r}
# Question and answer string
q_id <- c('video_viewing', 
          'q_answering', 
          'breaks', 
          'object_recognition',
          'exp_problems',
          'navigation',
          'object_time',
          'memory1',
          'strategy1', 
          'strategy2',
          'instructions')

questions_string <- c('Did you do anything else while watching the videos?',
  'Did you do your best to answer the questions correctly?',
  'Did you take breaks during the experiment?',
  'Did you recognise all objects in the videos and in the memory task? (If you can, please try describe the/those object(s) where you had problems briefly e.g. their shape/colour.)',
  'Did you experience any problems viewing the videos? Or problems in the experiment in general? (If yes, please elaborate.)',
  'Did the navigation feel too fast?',
  'Did you think the time the objects were visible was long enough?',
  'Did you anticipate there would be a memory test on the objects? If so, did you anticipate you would be asked about the order of the objects?',
  'Did you use any strategy to remember the objects and their order? One strategy for instance could be to recall the table an object was on and then to exclude options on that basis. (If yes, please elaborate.)',
  'Specifically, did you sometimes make responses based on the general memory when objects appeared in the video but not based on exactly knowing order of objects?',
  "Now, you've completed the task. Can we somehow improve our instructions? Please describe the instructions for memory task very briefly.")

questions <- data.frame(id = q_id,
                       question = questions_string)

answerQuestionID <- c(1, 1, 1,
                      2, 2, 2,
                      3, 3, 3,
                      4, 4, 4,
                      5, 5,
                      6, 6,
                      7, 7,
                      8, 8, 8,
                      9, 9,
                      10, 10, 10)

answerValue <- c('other_things', 'unattentive', 'attentive',
                 "did_best", "partly_random", "random",
                 "yes", "short_breaks", "no",
                 "all", "nearlyAll", "manyNot",
                 "yes", "no",
                 "yes", "no",
                 "yes", "no",
                 "expOrder", "expTest", "expNone",
                 "yes", "no",
                 "often", "rare", "no")

answerString <- c("Yes, at times I was busy with other things and missed parts of the videos.",
                  "I didn't do anything else, but did not always watch attentively.",
                  "No, I watched the whole video attentively.",
                  "Yes, I tried my best to answer everything correctly.",
                  "At least some of the time I answered randomly.",
                  "I answered randomly for the most part.",
                  "I took longer breaks.",
                  "I took some, but they were short (up to 2 minutes).",
                  "No, I completed the experiment in one go.",
                  "I recognised all.",
                  "I recognised nearly all.",
                  "I  didn't recognise many objects.",
                  "Yes.",
                  "No.",
                  "Yes.",
                  "No.",
                  "Yes.",
                  "No.",
                  "I anticipated I would be tested on order.",
                  "I anticipated there would be a test, but not which questions would be asked.",
                  "I didn’t anticipate memory would be tested.",
                  "Yes.",
                  "No.",
                  "Yes, often.",
                  "Yes but rarely.",
                  "No.")
```


```{r parseData2, echo = FALSE}
nQuestions     <- 10
folder         <- '/debrief/'
allFiles       <- list.files(paste0(exp3_path, folder))
allFiles_paths <- paste0(exp3_path, folder, allFiles)
nSub           <- length(allFiles_paths)

general_comments <- rep(NA_character_, nSub)
worker_ids       <- rep(NA, nSub)

for(i in 1:nSub){
  # Load JSON
  jsonString  <- readChar(allFiles_paths[i], file.info(allFiles_paths[i])$size)
  resultsList <- fromJSON(jsonString)
  
  # Get questions
  tempData              <- questions
  tempData$SubNum       <- i
  tempData$worker_id    <- resultsList$workerId
  tempData$answerValue  <- NA
  tempData$answerString <- NA
  tempData$survey       <- NA
  
  # Go through list of ith participant
  for(j in 1:nQuestions){
    # Assign answer value 
    tempData$answerValue[j] <- resultsList[[paste0('q', j)]]$answer
    
    # Get answer string by subsetting answer values belonging to jth question
    temp_answerStrings       <- answerString[which(answerQuestionID == j)]
    tempData$answerString[j] <- temp_answerStrings[which(answerValue[which(answerQuestionID == j)] == tempData$answerValue[j])]
    
    # Add content of text field if it exists
    if(!is.null(resultsList[[paste0('q', j)]]$survey)){
      tempData$survey[j] <- resultsList[[paste0('q', j)]]$survey
    }
  }
  
  # Bind to df
  if(i == 1){
    debriefData <- tempData
  } else{
    debriefData <- rbind(debriefData, tempData)
  }
  
  # Get general comments
  general_comments[i] <- resultsList$general_comments
  worker_ids[i]      <- resultsList$workerId
}

```


```{r fig12, fig.height = 27, fig.width = 10}
for(i in 1:nQuestions){
  tempSubset    <- debriefData[debriefData$id == q_id[i],]
  tempDF        <- data.frame(table(tempSubset$answerString))
  names(tempDF) <- c('Answer', 'Freq')

  bp  <- ggplot(tempDF, aes(x = "", y =  Freq, fill = Answer)) + geom_bar(width = 1, stat = "identity")
  tempPie <- bp + coord_polar("y", start = 0) + scale_fill_mrc() + 
    labs(x = '', y = '', title = paste(strwrap(questions_string[i], 60), collapse = "\n")) +
    theme(axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          panel.border = element_blank(),
          panel.grid = element_blank(),
          axis.ticks = element_blank(),
          plot.title = element_text(size = 8, face = "bold", hjust = 0.5),
          legend.position = "bottom",
          legend.direction = "vertical")
  assign(paste0('pie', i), tempPie)
}

plot_grid(pie1, pie2, pie3, pie4, pie5, pie6, pie7, pie8, pie9, pie10, ncol = 2, align = 'hv')
```


### Further comments regarding the questions
```{r, results = 'asis'}
for(i in 1:nrow(debriefData)){
  if(!(is.na(debriefData$survey[i]) | debriefData$survey[i] == "")){
    printText2rmarkdown(paste("<strong>Subject:", debriefData$worker_id[i], "</strong> "))
    printText2rmarkdown(paste0("<i>", debriefData$question[i], "</i>:\n"))
    printText2rmarkdown(paste0(debriefData$survey[i], "\n"))
  }
}
```

### General comments
```{r, results = 'asis'}
for(i in 1:length(general_comments)){
  if(!(is.na(general_comments[i]) | general_comments[i] == "")){
    printText2rmarkdown(paste("<strong>Subject:", worker_ids[i], "</strong>\n"))
    printText2rmarkdown(paste0(general_comments[i], "\n"))
  }
}
```
