---
title: "Analysis of memory task"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE, message = FALSE, warning = FALSE)
library(rjson)
library(ggplot2)
library(MRColour)
library(cowplot)
library(knitr)
library(plyr)
library(reshape2)
theme_set(theme_grey()) # Important to retain the ggplot theme
library(ez)
```

```{r loadData, echo = FALSE}
# Load all data
prefix         <- 'U:/Projects/boundaryVR/analysis/batch2/memoryTask/'
allFiles       <- list.files(paste(prefix, sep = ''))
allFiles_paths <- paste(prefix, allFiles, sep = '')
n              <- length(allFiles_paths)

for(i in 1:n){
  tempDF <- read.csv(allFiles_paths[i], header = TRUE, na.strings = '')
  # To be able to visualise
  tempDF$stimulus         <- NULL 
  tempDF$success          <- NULL
  tempDF$trial_type       <- NULL
  tempDF$internal_node_id <- NULL
  
  # Temporal order memory
  temporalOrder    <- subset(tempDF, test_part == 'temporalOrder')
  temporalOrder$rt <- as.numeric(as.character(temporalOrder$rt))
  # Recode key presses
  response      <- rep(NA, dim(temporalOrder)[1])
  response[temporalOrder$key_press == 49] <- 1
  response[temporalOrder$key_press == 50] <- 2
  response[temporalOrder$key_press == 51] <- 3
  temporalOrder$response                  <- response
  
  # Calcalate accuracy 
  accuracy <- rep(NA, dim(temporalOrder)[1])
  accuracy[temporalOrder$response == temporalOrder$corr_resp] <- 1
  accuracy[temporalOrder$response != temporalOrder$corr_resp] <- 0
  temporalOrder$accuracy <- accuracy
   
  # Room type question
  roomType      <- subset(tempDF, test_part == 'roomType')
  roomType$rt   <- as.numeric(as.character(roomType$rt))
  
  # Recode key presses
  response      <- rep(NA, dim(roomType)[1])
  response[roomType$key_press == 49] <- 1
  response[roomType$key_press == 50] <- 2
  roomType$response                  <- response
  
  # Calculate accuracy
  accuracy <- rep(NA, dim(roomType)[1])
  accuracy[roomType$response == roomType$corr_resp] <- 1
  accuracy[roomType$response != roomType$corr_resp] <- 0
  roomType$accuracy <- accuracy
  
  
  # Table question
  tableNum      <- subset(tempDF, test_part == 'tableNum')
  tableNum$rt   <- as.numeric(as.character(tableNum$rt))
  
  # Recode keypresses
  response      <- rep(NA, dim(tableNum)[1])
  response[tableNum$key_press == 49] <- 3 # for key press 1
  response[tableNum$key_press == 50] <- 2 # for key press 2
  tableNum$response                  <- response
  
  # Calculate accuracy
  accuracy <- rep(NA, dim(tableNum)[1])
  accuracy[tableNum$response == tableNum$corr_resp] <- 1
  accuracy[tableNum$response != tableNum$corr_resp] <- 0
  tableNum$accuracy <- accuracy
  
  # Create or bind to data.frame
  if(i == 1){
    temporalOrder_comb    <- temporalOrder
    temporalOrder_comb$id <- i
    roomType_comb         <- roomType
    roomType_comb$id      <- i
    tableNum_comb         <- tableNum
    tableNum_comb$id      <- i
  } else {
    temporalOrder$id   <- i
    temporalOrder_comb <- rbind(temporalOrder_comb, temporalOrder)
    roomType$id        <- i
    roomType_comb      <- rbind(roomType_comb, roomType)
    tableNum$id        <- i
    tableNum_comb      <- rbind(tableNum_comb, tableNum)
  }
}

# Convert to id factor
temporalOrder_comb$id <- as.factor(temporalOrder_comb$id)
roomType_comb$id      <- as.factor(roomType_comb$id)
tableNum_comb$id      <- as.factor(tableNum_comb$id)
```

# Analyse data
## Analysis of raw data
### Temporal order memory
```{r}
# Aggregate data
temporalOrder_agg <- ddply(temporalOrder_comb, c('id', 'context'), summarise, 
                           n = length(rt),
                           acc = mean(accuracy), 
                           rt = mean(rt))

afcPlot <- ggplot(temporalOrder_agg, aes(x = context, y = acc)) + 
  geom_boxplot(alpha = 0.5,outlier.shape = NA) + 
  geom_jitter(width = 0.1) +
  geom_hline(yintercept = 1/3) +
  annotate('text', x = 2, y = 0.31, label = 'Chance') +
  labs(y = '3AFC accuracy', x = "Room type", title = 'Temporal Order')


rtPlot <- ggplot(temporalOrder_agg, aes(x = context, y = rt)) + 
  geom_boxplot(alpha = 0.5, outlier.shape = NA) + 
  geom_jitter(width = 0.5) +
  labs(y = 'RT (msec)', x = "Room type", title = '')

plot_grid(afcPlot, rtPlot)
```

As can be seen above, some participants seems to significantly perform below chance. To show this, I simulated a null distribution (see below). In an ANOVA, there were no difference between the conditions:
```{r}
ezANOVA(temporalOrder_agg, dv = acc, wid = id, within = context)
```


### Room and table question
```{r}
#Aggregate data
roomType_comb_agg <- ddply(roomType_comb, c('id'), summarise, acc = mean(accuracy), rt = mean(rt))
tableNum_comb_agg <- ddply(tableNum_comb, c('id'), summarise, acc = mean(accuracy), rt = mean(rt))

roomTable_agg <- data.frame(id = rep(1:n, 2),
                            Type = rep(c('Room', 'Table'), each = n),
                            acc = c(roomType_comb_agg$acc, tableNum_comb_agg$acc))

ggplot(roomTable_agg, aes(x = Type, y = acc)) + 
  geom_boxplot(alpha = 0.5,outlier.shape = NA) + 
  geom_jitter(width = 0.1) +
  geom_hline(yintercept = 0.5) +
  annotate('text', x = 1.5, y = 0.48, label = 'Chance') +
  labs(y = 'Accuracy', x = "Memory type", title = 'Memory for room type and table')

```

While performance for the room task was not above chance

```{r}
t.test(roomType_comb_agg$acc -0.5)
```

the performance for the table question was:

```{r}
t.test(tableNum_comb_agg$acc - 0.5)
```


# Simulating a null distribution for temporal memory
With random guesses participants should get an average accuracy of 1/3 in the 3AFC task. However, some participants' accuracy is extremely low. To exclude those participants that actually perform below chance, I simulated a null distribution (N = 10000) for each condition since each condition has different number of trials. 

```{r}
# Simulation parameters
nSims     <- 10000
nTrials   <- c(39, 20, 19) # trials per condiiton
accDist1  <- c()
accDist2  <- c()
accDist3  <- c()

# Simulation
for(i in 1:nSims){
  accDist1[i] <- mean(rbinom(nTrials[1], 1, 1/3))
  accDist2[i] <- mean(rbinom(nTrials[2], 1, 1/3))
  accDist3[i] <- mean(rbinom(nTrials[3], 1, 1/3))
}

# Bind to df
accDists <- data.frame(Context = rep(c('across', 'within-no-walls', 'within-walls'), each = nSims),
                       Accuracy = c(accDist1, accDist2, accDist3))
cutOffs  <-  data.frame(Context = c('across', 'within-no-walls', 'within-walls'),
                        Accuracy = c(quantile(accDist1, 0.05),
                                     quantile(accDist2, 0.05),
                                     quantile(accDist3, 0.05)))

# Plot distributions
ggplot(accDists, aes(x = Accuracy)) + 
  facet_grid(.~ Context) + 
  geom_histogram() + 
  geom_vline(data = cutOffs, aes(xintercept = Accuracy), linetype = 'dashed')
```

Above, you see the null distribution that we would expect if participants answer randomly. We will re-ran the analysis using the following cut-offs

```{r}
kable(cutOffs)
```

and exclude anyone scoring below any of these cut-offs. As can be seen above, the trial number per condition influences the cut-off. This is because with a smaller trial number, fewer response patterns are possible.

```{r}
nTrials        <- 5:100
percentile_5th <- c()

# Run simulation
for(i in 1:length(nTrials)){
  tempDist <- c()
  
  for(j in 1:nSims){
    tempDist[j] <- mean(rbinom(nTrials[i], 1, 1/3))
  }
  percentile_5th[i] <- quantile(tempDist, 0.05)
}

trial_sim <- data.frame(nTrials = nTrials,
                        per_5th = percentile_5th)

ggplot(trial_sim, aes(x = nTrials, y = per_5th)) + 
  geom_point() +
  labs(x = 'Number of trials', 
       y = '5th percentile', 
       title = 'Cut-off values as a function of trial number')
```

The graphic above shows the 5th percentile varies as function of the trial number. For situations with small trial numbers, lower values are still probable under the null distribution. This is because the probability of getting all trials right is higher if you have only 2 trials compared if you have a 100 trials. Hence, I would argue it's appropriate to have different cut-offs for the different conditions. While the across condition has 39 trials, the within-walls only has 19. If participants randomly guessed, I expect different null distributions even though in both cases the success probability is 1/3.

# Exlcuding participants that are below 5th percentile of null distribution
## With condition specific cut-offs
```{r}
# Create exlusion var and set to 0 as default
exclude <- rep(0, n)
context <- c('across', 'within-no-walls', 'within-walls')

for(i in 1:dim(temporalOrder_agg)[1]){
  # Exclude if accuracy is below cut-off for given condition
  if(temporalOrder_agg$acc[i] < cutOffs$Accuracy[cutOffs$Context == temporalOrder_agg$context[i]]){
    exclude[temporalOrder_agg$id[i]] <- 1
  }
}

# Create subset
temporalOrder_agg$exclude <- rep(exclude, each = 3)
temporalOrder_agg_sub     <- temporalOrder_agg[temporalOrder_agg$exclude == 0, ]
```

Based on the cut-offs, I excluded `r sum(exclude)` participants from the analysis. 

# Temporal order memory on subset
```{r}
# Aggregate data
afcPlot <- ggplot(temporalOrder_agg_sub, aes(x = context, y = acc)) + 
  geom_boxplot(alpha = 0.5,outlier.shape = NA) + 
  geom_jitter(width = 0.1) +
  geom_hline(yintercept = 1/3) +
  annotate('text', x = 2, y = 0.31, label = 'Chance') +
  labs(y = '3AFC accuracy', x = "Room type", title = 'Temporal Order')


rtPlot <- ggplot(temporalOrder_agg_sub, aes(x = context, y = rt)) + 
  geom_boxplot(alpha = 0.5, outlier.shape = NA) + 
  geom_jitter(width = 0.5) +
  labs(y = 'RT (msec)', x = "Room type", title = '')

plot_grid(afcPlot, rtPlot)
```

However, there are still no significant difference between the conditions:

```{r}
ezANOVA(temporalOrder_agg_sub, dv = acc, wid = id, within = context)
```

Unexpectedly, the effect size increased with increased memory for the across and the within-walls condition. 

## Cut-off across conditions
Overall, there are 78 trials in the experiment. Below chance performance for that case would be `r trial_sim[trial_sim$nTrials == 78, 2]`. 

```{r}
temporalOrder_agg2 <- ddply(temporalOrder_comb, c('id'), summarise, 
                           n = length(accuracy),
                           acc = mean(accuracy))

# How many participants are excluded becuase they're below or equal to that cut-off
cutOff78 <- trial_sim[trial_sim$nTrials == 78, 2]
exclude  <- temporalOrder_agg2$id[which(temporalOrder_agg2$acc <= cutOff78)]
```

There is `r length(exclude)` participant(s), to which that applies. If we exclude this participant from the analysis.

```{r}
temporalOrder_agg_sub2 <- temporalOrder_agg[temporalOrder_agg$id != exclude, ]
```


# Temporal order memory on subset
```{r}
# Aggregate data
afcPlot <- ggplot(temporalOrder_agg_sub2, aes(x = context, y = acc)) + 
  geom_boxplot(alpha = 0.5,outlier.shape = NA) + 
  geom_jitter(width = 0.1) +
  geom_hline(yintercept = 1/3) +
  annotate('text', x = 2, y = 0.31, label = 'Chance') +
  labs(y = '3AFC accuracy', x = "Room type", title = 'Temporal Order')


rtPlot <- ggplot(temporalOrder_agg_sub2, aes(x = context, y = rt)) + 
  geom_boxplot(alpha = 0.5, outlier.shape = NA) + 
  geom_jitter(width = 0.5) +
  labs(y = 'RT (msec)', x = "Room type", title = '')

plot_grid(afcPlot, rtPlot)
```

As expected, excluding that participant didn't change the interpretation. 

```{r}
ezANOVA(temporalOrder_agg_sub2, dv = acc, wid = id, within = context)
```

# Additional analysis after rabble
During rabble, we came up with two additional analyses to figure out why our performance is so low. 

## Is there a bias towards one foil?
In the first step, I need to add the respective information from the [R-script](https://github.com/JAQuent/boundaryVR/blob/master/onlineExperiment/r_supportFiles/createTrials.R) that creates the trial information. 
```{r loadData2, echo = FALSE}
# Load trial information
load("U:/Projects/boundaryVR/onlineExperiment/r_supportFiles/trialData_20191120_174756.RData")
# Note that counterbalancing in that images goes from 1 to 8, while it goes from 0 to 7 in the javascript
# files.

# Order trial information
trials_cond5 <- trials_cond5[order(trials_cond5$objNum),]
trials_cond6 <- trials_cond6[order(trials_cond6$objNum),]
trials_cond7 <- trials_cond7[order(trials_cond7$objNum),]
trials_cond8 <- trials_cond8[order(trials_cond8$objNum),]

# Load all data
prefix         <- 'U:/Projects/boundaryVR/analysis/batch2/memoryTask/'
allFiles       <- list.files(paste(prefix, sep = ''))
allFiles_paths <- paste(prefix, allFiles, sep = '')
n              <- length(allFiles_paths)

for(i in 1:n){
  tempDF <- read.csv(allFiles_paths[i], header = TRUE, na.strings = '')
  # To be able to visualise
  tempDF$stimulus         <- NULL 
  tempDF$success          <- NULL
  tempDF$trial_type       <- NULL
  tempDF$internal_node_id <- NULL
  
  # Temporal order memory
  temporalOrder <- subset(tempDF, test_part == 'temporalOrder')
  
  # Sort by objectNumber
  temporalOrder <- temporalOrder[order(temporalOrder$probe),]
  
  # get trialinfo and add to temporalOrder
  cond <- temporalOrder$condition[1] + 1 # to correct for difference
  temporalOrder$foil1Pos <- get(paste0("trials_cond", cond))$foil1Pos
  temporalOrder$foil2Pos <- get(paste0("trials_cond", cond))$foil2Pos
  
  temporalOrder$rt <- as.numeric(as.character(temporalOrder$rt))
  # Recode key presses
  response      <- rep(NA, dim(temporalOrder)[1])
  response[temporalOrder$key_press == 49] <- 1
  response[temporalOrder$key_press == 50] <- 2
  response[temporalOrder$key_press == 51] <- 3
  temporalOrder$response                  <- response
  
  # Calcalate accuracy 
  accuracy <- rep(NA, dim(temporalOrder)[1])
  accuracy[temporalOrder$response == temporalOrder$corr_resp] <- 1
  accuracy[temporalOrder$response != temporalOrder$corr_resp] <- 0
  temporalOrder$accuracy <- accuracy
  
  # Create variable that desribe whether target, foil1, foil2 was choosen
  choice <- rep('Target', dim(temporalOrder)[1])
  choice[temporalOrder$response == temporalOrder$foil1Pos] <- 'Foil 1'
  choice[temporalOrder$response == temporalOrder$foil2Pos] <- 'Foil 2'
  temporalOrder$choice <- choice
   
  # Room type question
  roomType      <- subset(tempDF, test_part == 'roomType')
  roomType$rt   <- as.numeric(as.character(roomType$rt))
  
  # Recode key presses
  response      <- rep(NA, dim(roomType)[1])
  response[roomType$key_press == 49] <- 1
  response[roomType$key_press == 50] <- 2
  roomType$response                  <- response
  
  # Calculate accuracy
  accuracy <- rep(NA, dim(roomType)[1])
  accuracy[roomType$response == roomType$corr_resp] <- 1
  accuracy[roomType$response != roomType$corr_resp] <- 0
  roomType$accuracy <- accuracy
  
  
  # Table question
  tableNum      <- subset(tempDF, test_part == 'tableNum')
  tableNum$rt   <- as.numeric(as.character(tableNum$rt))
  
  # Recode keypresses
  response      <- rep(NA, dim(tableNum)[1])
  response[tableNum$key_press == 49] <- 3 # for key press 1
  response[tableNum$key_press == 50] <- 2 # for key press 2
  tableNum$response                  <- response
  
  # Calculate accuracy
  accuracy <- rep(NA, dim(tableNum)[1])
  accuracy[tableNum$response == tableNum$corr_resp] <- 1
  accuracy[tableNum$response != tableNum$corr_resp] <- 0
  tableNum$accuracy <- accuracy
  
  # Create or bind to data.frame
  if(i == 1){
    temporalOrder_comb    <- temporalOrder
    temporalOrder_comb$id <- i
    roomType_comb         <- roomType
    roomType_comb$id      <- i
    tableNum_comb         <- tableNum
    tableNum_comb$id      <- i
  } else {
    temporalOrder$id   <- i
    temporalOrder_comb <- rbind(temporalOrder_comb, temporalOrder)
    roomType$id        <- i
    roomType_comb      <- rbind(roomType_comb, roomType)
    tableNum$id        <- i
    tableNum_comb      <- rbind(tableNum_comb, tableNum)
  }
}

# Convert to id factor
temporalOrder_comb$id <- as.factor(temporalOrder_comb$id)
roomType_comb$id      <- as.factor(roomType_comb$id)
tableNum_comb$id      <- as.factor(tableNum_comb$id)
```

```{r}
temporalOrder_comb_incorrect <- subset(temporalOrder_comb, temporalOrder_comb$accuracy == 0)
temporalOrder_foils <- ddply(temporalOrder_comb_incorrect, c('id'), 
                             summarise,
                             n   = length(choice),
                             foil1 = table(choice)[1],
                             foil2 = table(choice)[2])

# Create percentages
temporalOrder_foils$foil1 <- temporalOrder_foils$foil1 / temporalOrder_foils$n
temporalOrder_foils$foil2 <- temporalOrder_foils$foil2 / temporalOrder_foils$n

# Melt for plotting
temporalOrder_foils <- melt(temporalOrder_foils, id.vars =c("id"), measure.vars = c('foil1', 'foil2'))

# Plot
ggplot(temporalOrder_foils, aes(x = variable, y = value)) + 
  geom_boxplot(alpha = 0.5,outlier.shape = NA) + 
  geom_jitter(width = 0.1) +
  labs(y = 'Percentage of choice', x = '', title = 'Foil choice')
```

Foil 1 is behind the target and foil 2 is after the target. However, there is nearly no difference between the times foil 1 is choosen over foil 2 and vice versa.

## Analysis of participants that expected a memory test
Because I didn't save a participant ID for all output, I need to manually assign the results of the memory task to the debrief questionnaire data by renaming the filenames. 

```{r strings, echo = FALSE}
# Question and answer string
q_id <- c('video_viewing', 
          'q_answering', 
          'breaks', 
          'room_feeling1', 
          'room_feeling2', 
          'room_feeling3', 
          'object_recognition',
          'exp_problems',
          'navigation',
          'object_time',
          'memory1',
          'memory2', 
          'instructions')

questions_string <- c('Did you do anything else while watching the video?',
               'Did you do your best to answer the questions correctly?',
               'Did you take breaks during the experiment?',
               'Did rooms with a partition feel like they were a single room (similar to the room without a partition) \nor did they feel like two separate rooms? (Please elaborate below.)',
               'Did you feel it was harder/easier to remember the order of objects in the rooms without a partition \nrelative to those with a partition?',
               'When crossing from one part of the room to the next in a partitioned room, did that feel like you were \nmoving to a new room (a bit like walking through a door)?',
               'Did you recognise all objects in the video and in the memory task? (If you can, please try describe \nthe/those object(s) briefly.)',
               'Did you experience any problems viewing the videos? Or problems in the experiment in general? (If yes,\nplease elaborate.)',
               'Did the navigation feel too fast?',
               'Did you think the time the objects were visible was long enough?',
               'Did you anticipate there would be a memory test on the objects? If so, did you anticipate you would be \nasked about the order of the objects?',
               'Did you use any strategy to remember the objects and their order? (If yes, please elaborate.)',
               'Now, you\'ve completed the task. Can we somehow improve our instructions? (If yes, please elaborate.)')

questions <- data.frame(id = q_id,
                       question = questions_string)

answerQuestionID <- c(1, 1, 1, 2, 2, 2, 3, 3, 3, 4, 4, 4, 5 ,5, 5, 6, 6, 6, 7, 7, 7,
                      8, 8, 9, 9, 10, 10, 11, 11, 11, 12, 12, 13, 13)

answerValue <- c('other_things',
                 'unattentive',
                 'attentive',
                 'did_best',
                 'random',
                 'partly_random',
                 'yes',
                 'short_breaks',
                 'no',
                 'yes',
                 'cannot_say',
                 'no',
                 'easierWithout',
                 'noDiff',
                 'easierWith',
                 'yes',
                 'cannot_say',
                 'no',
                 'all',
                 'nearlyAll',
                 'manyNot',
                 'yes',
                 'no',
                 'yes',
                 'no',
                 'yes',
                 'no',
                 'expOrder',
                 'expTest',
                 'expNone',
                 'yes',
                 'no',
                 'yes',
                 'no')

answerString <- c('Yes, at times I was busy with other things and missed parts of the video.',
                  'I didn\'t do anything else, but did not always watch attentively.',
                  'No, I watched all the whole video attentively.',
                  'Yes, I tried my best to answer everything correctly.',
                  'I answered randomly for the most part.',
                  'At least some of the time I answered randomly.',
                  'Yes, I took breaks.',
                  'I took some, but they were short (up to 1 minute).',
                  'No, I completed the experiment in one go.',
                  'Yes, I both type of rooms felt like one.',
                  'I can\'t say.',
                  'No, the room with walls in the middle felt like two separate rooms.',
                  'It was easier without partition.',
                  'There was no diferrence.',
                  'It was easier with partition.',
                  'Yes, did feel like this.',
                  'I can\'t say.',
                  'No, I didn\'t feel like this.',
                  'I recognised all.',
                  'I recognised nearly all.',
                  'I  didn\'t recognise many objects.',
                  'Yes.',
                  'No.',
                  'Yes.',
                  'No.',
                  'Yes.',
                  'No.',
                  'I anticipated I would be tested on order.',
                  'I anticipated there would be a test, but not which questions would be asked.',
                  'I didn’t anticipate memory would be tested.',
                  'Yes.',
                  'No.',
                  'Yes.',
                  'No.')
```

```{r parseData, echo = FALSE}
nQuestions     <- 13
prefix         <- 'U:/Projects/boundaryVR/analysis/batch2/debrief/'
allFiles       <- list.files(paste(prefix, sep = ''))
allFiles_paths <- paste(prefix, allFiles, sep = '')
nSub           <- length(allFiles_paths)

general_comments <- rep(NA_character_, nSub)

for(i in 1:nSub){
  # Load JSON
  jsonString  <- readChar(allFiles_paths[i], file.info(allFiles_paths[i])$size)
  resultsList <- fromJSON(jsonString)
  
  # Get questions
  tempData              <- questions
  tempData$SubNum       <- i
  tempData$answerValue  <- NA
  tempData$answerString <- NA
  tempData$survey       <- NA
  
  # Go through list of ith participant
  for(j in 1:nQuestions){
    # Assign answer value 
    tempData$answerValue[j] <- resultsList[[paste0('q', j)]]$answer
    
    # Get answer string by subsetting answer values belonging to jth question
    temp_answerStrings       <- answerString[which(answerQuestionID == j)]
    tempData$answerString[j] <- temp_answerStrings[which(answerValue[which(answerQuestionID == j)] == tempData$answerValue[j])]
    
    # Add content of text field if it exists
    if(!is.null(resultsList[[paste0('q', j)]]$survey)){
      tempData$survey[j] <- resultsList[[paste0('q', j)]]$survey
    }
  }
  
  # Bind to df
  if(i == 1){
    debriefData <- tempData
  } else{
    debriefData <- rbind(debriefData, tempData)
  }
  
  # Get general comments
  general_comments[i] <- resultsList$general_comments
}

```

```{r}
# Get participants that expected memory task
expectedTest <- debriefData$SubNum[debriefData$id == 'memory1'] 
expectedTest <- expectedTest[debriefData$answerValue[debriefData$id == 'memory1'] != 'expNone']

# Create subset
temporalOrder_agg_sub <- temporalOrder_agg[temporalOrder_agg$id %in% expectedTest, ]

afcPlot <- ggplot(temporalOrder_agg_sub, aes(x = context, y = acc)) + 
  geom_boxplot(alpha = 0.5,outlier.shape = NA) + 
  geom_jitter(width = 0.1) +
  geom_hline(yintercept = 1/3) +
  annotate('text', x = 2, y = 0.31, label = 'Chance') +
  labs(y = '3AFC accuracy', x = "Room type", title = 'Temporal Order')


rtPlot <- ggplot(temporalOrder_agg_sub, aes(x = context, y = rt)) + 
  geom_boxplot(alpha = 0.5, outlier.shape = NA) + 
  geom_jitter(width = 0.5) +
  labs(y = 'RT (msec)', x = "Room type", title = '')

plot_grid(afcPlot, rtPlot)
```


